### 2025-09-22 paper/sec/evaluation.tex
first pass on negative cases

@@

        \hline
    \end{tabular}
    \caption{Categories of problematic example}
    \label{tab:ambiguita}
\end{table}

>>>>

Table~\ref{tab:problematic_cases} presents examples of problematic cases in which the system was asked to generate a valid
fluid expression.
In these cases, producing a valid expression is challenging because the input data (or the NL query) contains ambiguities
that prevent the construction of a well-formed expression.

For instance, in the \textit{missing-data} problem, the \InterpretationAgent should generate a function to compute
 the average of the emissions. However, the input data does not provide information for all months.

In such cases, the system was unable to generate a general expression and instead produced the expected value directly.

@@

        \hline
    \end{tabular}
    \caption{Categories of problematic example}
    \label{tab:problematic_cases}
\end{table}
